%------------------------------------------------------------
% resume.tex — Brian Hungerman
% Compile: pdflatex resume.tex
%------------------------------------------------------------
\documentclass[10pt,letterpaper]{article}

\usepackage[top=0.3in, bottom=0.25in, left=0.4in, right=0.4in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{paracol}
\usepackage[T1]{fontenc}
\usepackage{helvet}
\usepackage{microtype}

% ── Use Helvetica (sans-serif) as default ─────────────────
\renewcommand{\familydefault}{\sfdefault}

% ── All text black, all links black ───────────────────────
\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  pdfauthor={Brian Hungerman},
  pdftitle={Brian Hungerman -- Resume}
}

% ── Section headers: BOLD + thin black underline ──────────
\titleformat{\section}
  {\large\bfseries\MakeUppercase}
  {}
  {0pt}
  {}
  [\vspace{-6pt}{\hrule height 0.4pt}\vspace{2pt}]

\titlespacing*{\section}{0pt}{6pt}{3pt}

% ── Compact bullet lists ─────────────────────────────────
\setlist[itemize]{
  nosep, topsep=1pt, partopsep=0pt, parsep=0pt,
  itemsep=0pt, left=10pt, label={\small\textbullet}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\columnsep}{12pt}

% ══════════════════════════════════════════════════════════
\begin{document}

% ── HEADER ────────────────────────────────────────────────
\begin{minipage}[t]{0.58\textwidth}
  \vspace{0pt}
  {\fontsize{26}{30}\selectfont\bfseries Brian Hungerman}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.38\textwidth}
  \vspace{2pt}
  \raggedleft\small
  https://brianhungerman.com\\
  brianhungerman@gmail.com\\
  1 (425) 389-9642
\end{minipage}

\vspace{4pt}

% ── TWO COLUMNS ──────────────────────────────────────────
\columnratio{0.72}
\begin{paracol}{2}

% ══════════════ LEFT COLUMN ══════════════════════════════

\section*{Experience}

\textbf{Senior Software Engineer @ Applied Sciences (Microsoft)}\hfill Jan 2025 -- Present
\begin{itemize}
  \item Incubating novel A.I.\ user experiences with collaboration across W+D, MSR \& ID.
  \item Developing full-stack functional prototypes across web \& mobile platforms.
\end{itemize}
\vspace{1pt}

\textbf{Software Engineer @ A.I.\ Platform (Microsoft)}\hfill Jan 2020 -- Jan 2025
\begin{itemize}
  \item Shipped Online Endpoints to 50+ regions for Azure OpenAI, Copilot, Office \& 3p.
  \item Scaled cloud infrastructure to serve trillions of inferences/month w/ 6 9's SLA.
  \item Optimized Network Address Translation to reduce COGS by \$10 million/year.
  \item Completed security, privacy \& component governance audits as Security Champ.
  \item Spearheaded livesite process improvements via TSGs \& SOPs as DRI Champ.
  \item Implemented Envoy Proxy build pipeline w/ Bazel \& custom C++ filters, e.g.:
    \begin{itemize}[label={\small$\cdot$}, left=8pt, nosep, itemsep=0pt]
      \item SHA-256 Key-Based Authentication (KBA) filter w/ CORS preflight support.
      \item Azure Active Directory (AAD) authentication filter w/ LRU decision cache.
      \item Global Rate Limiting filter w/ Go microservice to pub/sub to Redis cache.
    \end{itemize}
  \item Set up runners \& telemetry pipelines in Azure Data Explorer, Kusto \& SQL.
  \item Shipped PowerBI \& Grafana dashboards to track platform metrics \& logs.
\end{itemize}
\vspace{1pt}

\textbf{Software Engineer Intern @ A.I.\ Platform (Microsoft)}\hfill May 2019 -- Aug 2019
\begin{itemize}
  \item Designed Jupyter notebook CI pipeline w/ Azure DevOps, ML SDK \& Functions.
\end{itemize}
\vspace{1pt}

\textbf{Software Engineer Intern @ Ventana (Roche)}\hfill May 2018 -- Dec 2018
\begin{itemize}
  \item Pushed feature-adds \& bug-fixes for MEAN stack digital pathology web app.
  \item Prototyped OpenSeaDragon-esque image renderer \& annotator in Pixi.JS.
  \item Modernized Nagios server monitoring w/ Icinga, Graphite \& Grafana.
\end{itemize}
\vspace{1pt}

\textbf{Director @ HackMerced IV (MLH)}\hfill May 2018 -- May 2019
\begin{itemize}
  \item Hosted non-profit collegiate hackathon for 300 students, fundraising \$20,000!
\end{itemize}
\vspace{1pt}

\textbf{Web Developer @ CITRIS \& Banatao Institute (UCM)}\hfill May 2017 -- Dec 2018
\begin{itemize}
  \item Developed GitOps content management system (CMS) via jQuery \& CSV files to
        replace Drupal CMS, hosting via GitHub Pages: https://citris.ucmerced.edu.
\end{itemize}
\vspace{1pt}

\textbf{Instructor @ Summer of Game Design (MVHS)}\hfill Jun 2015 -- Jul 2016
\begin{itemize}
  \item Co-founded non-profit game programming summer camp, fundraising \$25,000!
\end{itemize}

% ── RESEARCH & EDUCATION ─────────────────────────────────
\section*{Research \& Education}

\textbf{Bachelor of Science @ University of California, Merced}\hfill Aug 2016 -- Dec 2019
\begin{itemize}
  \item Computer Science \& Engineering, \textit{magna cum laude} (GPA 3.74)
\end{itemize}
\vspace{1pt}

\textbf{Lead Research Assistant @ VICE Lab (UCM)}\hfill Aug 2018 -- Dec 2019
\begin{itemize}
  \item Led team to develop heuristic \& ML scripts in Google Earth Engine to model \&
        predict California's agricultural fallowing via Earth observation satellite data.
  \item Onboarded lab to GitHub \& wrote open-sourced scripts in Python, C\# \& R.
  \item Refurbished lab's website, hosting via GitHub Pages: https://vicelab.net.
\end{itemize}
\vspace{1pt}

\textbf{Research Assistant @ ANDES Lab (UCM)}\hfill Jan 2019 -- May 2019
\begin{itemize}
  \item Visualized InfluxDB data for HVAC predictive control system in Python, Grafana.
\end{itemize}
\vspace{1pt}

\textbf{Research Assistant @ SAIL + MACES (UCM \& NASA MUREP)}\hfill Aug 2017 -- May 2018
\begin{itemize}
  \item Debugged code to 3D-print Fermi surfaces via Marching cubes in Fortran90.
\end{itemize}

% ══════════════ RIGHT COLUMN ═════════════════════════════
\switchcolumnxzz

\small

\textbf{Languages}\hfill\textit{years}\\[2pt]
\hspace{4pt}C / C++ / C\#\hfill 8\\
\hspace{4pt}Python\hfill 6\\
\hspace{4pt}JavaScript / TS\hfill 4\\
\hspace{4pt}Golang / Rust\hfill 2\\
\hspace{4pt}Java / Kotlin\hfill 2\\[4pt]
\textbf{Frameworks}\hfill\textit{years}\\[2pt]
\hspace{4pt}Azure / .NET\hfill 6\\
\hspace{4pt}MEAN / MERN\hfill 2\\
\hspace{4pt}LAMP / Drupal\hfill 2\\[4pt]
\textbf{Programs}\hfill\textit{years}\\[2pt]
\hspace{4pt}Unity3D\hfill 8\\
\hspace{4pt}Docker / K8s\hfill 4\\
\hspace{4pt}Android Studio\hfill 2

\section*{Projects}

\small

\hspace{4pt}\textbf{Iterate}\\
\hspace{4pt}\textit{``Code Mobilized''}\\[3pt]
\hspace{4pt}\textbf{BitNaughts}\\
\hspace{4pt}\textit{``Code Gamified''}\\[3pt]
\hspace{4pt}\textbf{MARP}\\
\hspace{4pt}\textit{``\ldots''}

\section*{Awards}

\small

\hspace{4pt}\textbf{Microsoft Hackathon '20}\\
\hspace{4pt}\textit{HackADuo Finalist}\\[2pt]
\hspace{4pt}\textbf{ValleyHacks '19}\\
\hspace{4pt}\textit{First Place}\\[2pt]
\hspace{4pt}\textbf{SLOHacks '19}\\
\hspace{4pt}\textit{Best Google Cloud}\\[2pt]
\hspace{4pt}\textbf{Mobile App Challenge '18}\\
\hspace{4pt}\textit{\$2,000 Finalist Prize}\\[2pt]
\hspace{4pt}\textbf{CitrusHack '18}\\
\hspace{4pt}\textit{Third Place}\\[2pt]
\hspace{4pt}\textbf{SDHacks '18}\\
\hspace{4pt}\textit{Third Place}\\[2pt]
\hspace{4pt}\textbf{SacHacks '18}\\
\hspace{4pt}\textit{Second Place}\\[2pt]
\hspace{4pt}\textbf{HackDavis '18}\\
\hspace{4pt}\textit{Best Environment}\\[2pt]
\hspace{4pt}\textbf{HackFresno '18}\\
\hspace{4pt}\textit{Best Hardware}\\[2pt]
\hspace{4pt}\textbf{Mobile App Challenge '17}\\
\hspace{4pt}\textit{\$5,000 Grand Prize}\\[2pt]
\hspace{4pt}\textbf{HackMerced '17}\\
\hspace{4pt}\textit{Best Design}

\end{paracol}

\end{document}
