% resume-one-page-bible.tex — Brian Hungerman
% Content from resume2.tex, styled with resume-bible.tex aesthetics
% Compile with XeLaTeX or LuaLaTeX for custom font support
% =========================================================

\documentclass[10pt,letterpaper]{article}

% ----- Page Geometry (letter, tight margins for one-page) -----
\usepackage[top=0.2in, bottom=0.2in, left=0.38in, right=0.38in]{geometry}

% ----- Font Setup (requires XeLaTeX/LuaLaTeX) -----
\usepackage{fontspec}
\usepackage{microtype}

% Main body font — Old Standard TT (Google Fonts)
\setmainfont{Old Standard TT}[
    UprightFont = *-Regular,
    BoldFont = *-Bold,
    ItalicFont = *-Italic,
    FakeBold = 6
]

% Title font — Cinzel (Google Fonts)
\newfontfamily\titlefont{Cinzel}[
    UprightFont = *-Regular,
    BoldFont = *-Bold,
    FakeBold = 8
]

% Decorative title font — Cinzel Decorative
\newfontfamily\decorativefont{Cinzel Decorative}[
    UprightFont = *-Regular,
    BoldFont = *-Bold,
    FakeBold = 5
]

% ----- Packages -----
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{paracol}
\usepackage{lettrine}
\usepackage{GoudyIn}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{calc}

% Colors (from resume-bible.tex)
\definecolor{bloodred}{RGB}{138, 3, 3}
\definecolor{inkblack}{RGB}{30, 30, 30}
\color{inkblack}

\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  pdfauthor={Brian Hungerman},
  pdftitle={Brian Hungerman -- Resume}
}

% \speech = italicized proper nouns (bible.tex style, replaces \semi)
\newcommand{\speech}[1]{\textit{#1}}

% Horizontal rule (bible-style divider)
\newcommand{\divider}{%
    \begin{center}
    \rule{0.4\textwidth}{1.5pt}
    \end{center}
}

% Drop cap settings — Goudy Initialen decorative font
\renewcommand{\LettrineFontHook}{\GoudyInfamily}
\renewcommand{\LettrineTextFont}{\normalfont}
\setcounter{DefaultLines}{2}
\renewcommand{\DefaultLoversize}{0.1}
\renewcommand{\DefaultLraise}{0.1}
\setlength{\DefaultFindent}{3pt}
\setlength{\DefaultNindent}{0pt}

% ----- Section headers: bible-style left-justified with dividers -----
\titleformat{\section}
  {\titlefont\normalsize\raggedright}
  {}
  {0pt}
  {\vspace{-2pt}\hrule height 0.8pt\vspace{4pt}}

\titlespacing*{\section}{0pt}{6pt}{2pt}

% ----- Tight bullet lists (bible-style cdot) -----
\setlist[itemize]{
  nosep, topsep=0pt, partopsep=0pt, parsep=0pt,
  itemsep=0pt, left=8pt, label={$\cdot$},
  before=\vspace{-2pt}, after=\vspace{0pt}
}
\setlist[itemize,2]{
  nosep, topsep=0pt, partopsep=0pt, parsep=0pt,
  itemsep=0pt, left=10pt, label={$\cdot$}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\columnsep}{10pt}
\setlength{\columnseprule}{0.4pt}

% ═══════════════════════════════════════════════════════════════
\begin{document}

% ── HEADER ────────────────────────────────────────────────────
\begin{minipage}[t]{0.62\textwidth}
  \vspace{0pt}
  {\decorativefont\fontsize{24}{28}\selectfont\bfseries Brian Hungerman}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.34\textwidth}
  \vspace{4pt}
  \raggedleft\small
  https://brianhungerman.com\\
  brianhungerman@gmail.com\\
  1 (425) 389-9642
\end{minipage}

\vspace{1pt}

% ── TWO COLUMNS ──────────────────────────────────────────────
\columnratio{0.77}
\begin{paracol}{2}

% ═══════════════ LEFT COLUMN ═══════════════════════════════════

{\decorativefont\fontsize{12}{14}\selectfont\bfseries Experience}
\vspace{-2pt}\hrule height 0.8pt\vspace{4pt}

\lettrine[lines=2]{S}{enior} {\titlefont Software Engineer @ Applied Sciences, Microsoft}\hfill{\small\textit{2025}}
\begin{itemize}
  \item Incubating novel A.I.\ user experiences with collaboration across W+D, MSR \& ID.
  \item Developing full-stack functional prototypes across web \& mobile platforms.
\end{itemize}
\vspace{3pt}
\lettrine[lines=2]{S}{oftware} {\titlefont Engineer @ A.I.\ Platform, Microsoft}\hfill{\small\textit{2020 -- 2025}}
\begin{itemize}
  \item Shipped \speech{Online Endpoints} to 50+ regions for \speech{Azure OpenAI}, \speech{Copilot}, \speech{Office} \& 3p.
  \item Scaled cloud infrastructure to serve trillions of inferences/month w/ 6 9's \speech{SLA}.
  \item Optimized \speech{Network Address Translation} to reduce \speech{COGS} by \$10 million/year.
  \item Completed security, privacy \& component governance audits as \speech{Security Champ}.
  \item Spearheaded livesite process improvements via \speech{TSGs} \& \speech{SOPs} as \speech{DRI Champ}.
  \item Implemented \speech{Envoy Proxy} build pipeline w/ \speech{Bazel} \& custom \speech{C++} filters, e.g.:
  \begin{itemize}
      \item \speech{SHA-256 Key-Based Authentication (KBA)} filter w/ \speech{CORS} preflight support.
      \item \speech{Azure Active Directory (AAD)} authentication filter w/ \speech{LRU} decision cache.
      \item \speech{Global Rate Limiting} filter w/ \speech{Go} microservice to pub/sub to \speech{Redis} cache.
  \end{itemize}
  \item Set up runners \& telemetry pipelines in \speech{Azure Data Explorer}, \speech{Kusto} \& \speech{SQL}.
  \item Shipped \speech{PowerBI} \& \speech{Grafana} dashboards to track platform metrics \& logs.
\end{itemize}
\vspace{3pt}
\lettrine[lines=2]{S}{oftware} {\titlefont Engineer Intern @ A.I.\ Platform, Microsoft}\hfill{\small\textit{2019}}
\begin{itemize}
  \item Designed \speech{Jupyter} notebook \speech{CI} pipeline w/ \speech{Azure DevOps}, \speech{ML SDK} \& \speech{Functions}.
\end{itemize}
\vspace{3pt}
\lettrine[lines=2]{S}{oftware} {\titlefont Engineer Intern @ Ventana, Roche}\hfill{\small\textit{2018}}
\begin{itemize}
  \item Pushed feature-adds \& bug-fixes for \speech{MEAN} stack digital pathology web app.
  \item Prototyped \speech{OpenSeaDragon}-esque image renderer \& annotator in \speech{Pixi.JS}.
  \item Modernized \speech{Nagios} server monitoring w/ \speech{Icinga}, \speech{Graphite} \& \speech{Grafana}.
\end{itemize}
\vspace{3pt}
\lettrine[lines=2]{D}{irector} {\titlefont @ HackMerced IV, Major League Hacking}\hfill{\small\textit{2018 -- 2019}}
\begin{itemize}
  \item Hosted non-profit collegiate hackathon for 300 students, fundraising \$20,000!
\end{itemize}
\vspace{3pt}
\lettrine[lines=2]{W}{eb} {\titlefont Developer @ CITRIS \& Banatao Institute, UCM}\hfill{\small\textit{2017 -- 2018}}
\begin{itemize}
  \item Developed \speech{GitOps} content management system (\speech{CMS}) via \speech{jQuery} \& \speech{CSV} files to replace \speech{Drupal} \speech{CMS}, hosting via \speech{GitHub Pages}: https://citris.ucmerced.edu.
\end{itemize}
\vspace{3pt}
\lettrine[lines=2]{I}{nstructor} {\titlefont @ Summer of Game Design, MVHS}\hfill{\small\textit{2015 -- 2016}}
\begin{itemize}
  \item Co-founded non-profit game programming summer camp, fundraising \$25,000!
\end{itemize}

{\decorativefont\fontsize{12}{14}\selectfont\bfseries Research \& Education}
\vspace{-2pt}\hrule height 0.8pt\vspace{4pt}

\lettrine[lines=2]{B}{achelor} {\titlefont of Science @ University of California, Merced}\hfill{\small\textit{2016 -- 2019}}
\begin{itemize}
  \item Computer Science \& Engineering, \textit{magna cum laude} (GPA 3.74)
\end{itemize}
\vspace{3pt}
\lettrine[lines=2]{L}{ead} {\titlefont Research Assistant @ VICE Lab, UCM}\hfill{\small\textit{2018 -- 2019}}
\begin{itemize}
  \item Led team to develop heuristic \& \speech{ML} scripts in \speech{Google Earth Engine} to model \& predict California's agricultural fallowing via Earth observation satellite data.
  \item Onboarded lab to \speech{GitHub} \& wrote open-sourced scripts in \speech{Python}, \speech{C\#} \& \speech{R}.
  \item Refurbished lab's website, hosting via \speech{GitHub Pages}: https://vicelab.net.
\end{itemize}
\vspace{3pt}
\lettrine[lines=2]{R}{esearch} {\titlefont Assistant @ ANDES Lab, UCM}\hfill{\small\textit{2019}}
\begin{itemize}
  \item Visualized \speech{InfluxDB} data for \speech{HVAC} predictive control system in \speech{Python}, \speech{Grafana}.
\end{itemize}
\vspace{3pt}
\lettrine[lines=2]{R}{esearch} {\titlefont Assistant @ SAIL + MACES, UCM \& NASA MUREP}\hfill{\small\textit{2017 -- 2018}}
\begin{itemize}
  \item Debugged code to 3D-print \speech{Fermi} surfaces via \speech{Marching cubes} in \speech{Fortran90}.
\end{itemize}

% ═══════════════ RIGHT COLUMN ═══════════════════════════════════
\switchcolumn

{\decorativefont\fontsize{12}{14}\selectfont\bfseries Skills}
\vspace{-2pt}\hrule height 0.8pt\vspace{4pt}

{\fontsize{8pt}{10pt}\selectfont
\lettrine[lines=2]{L}{anguages:\ }
C / C++ / C\# (8 yrs);
\speech{Python} (6 yrs);
JS / TS (4 yrs);
\speech{Golang} / \speech{Rust} (2 yrs);
\speech{Java} / \speech{Kotlin} (2 yrs).

\vspace{2pt}
\lettrine[lines=2]{F}{rame-works:\ }
\speech{Azure} / .NET (6 yrs);
\speech{MEAN} / \speech{MERN} (2 yrs);
\speech{LAMP} / \speech{Drupal} (2 yrs).

\vspace{2pt}
\lettrine[lines=2]{P}{rograms:\ }
\speech{Unity3D} (8 yrs);
\speech{Docker} / K8s (4 yrs);
\speech{Android Studio} (2 yrs).
}

{\decorativefont\fontsize{12}{14}\selectfont\bfseries Projects}
\vspace{-2pt}\hrule height 0.8pt\vspace{4pt}

{\fontsize{8pt}{10pt}\selectfont
\lettrine[lines=2]{I}{terate} --- \textit{``Code Mobilized''}

\vspace{2pt}
\lettrine[lines=2]{B}{it-Naughts} --- \textit{``Code Gamified''}

\vspace{2pt}
\lettrine[lines=2]{M}{ARP} --- \textit{``\ldots''}
}

{\decorativefont\fontsize{12}{14}\selectfont\bfseries Awards}
\vspace{-2pt}\hrule height 0.8pt\vspace{4pt}

{\fontsize{8pt}{10pt}\selectfont
\lettrine[lines=2]{M}{icrosoft} Hackathon '20\\
\hfill\textit{HackADuo Finalist}\\[2pt]
\lettrine[lines=2]{V}{alley-Hacks} '19\\
\hfill\textit{First Place}\\[2pt]
\lettrine[lines=2]{S}{LO-Hacks} '19\\
\hfill\textit{Best Google Cloud}\\[2pt]
\lettrine[lines=2]{M}{obile} App Challenge '18\\
\hfill\textit{\$2,000 Finalist Prize}\\[2pt]
\lettrine[lines=2]{C}{itrus-Hack} '18\\
\hfill\textit{Third Place}\\[2pt]
\lettrine[lines=2]{S}{D-Hacks} '18\\
\hfill\textit{Third Place}\\[2pt]
\lettrine[lines=2]{S}{ac-Hacks} '18\\
\hfill\textit{Second Place}\\[2pt]
\lettrine[lines=2]{H}{ack-Davis} '18\\
\hfill\textit{Best Environment}\\[2pt]
\lettrine[lines=2]{H}{ack-Fresno} '18\\
\hfill\textit{Best Hardware}\\[2pt]
\lettrine[lines=2]{M}{obile} App Challenge '17\\
\hfill\textit{\$5,000 Grand Prize}\\[2pt]
\lettrine[lines=2]{H}{ack-Merced} '17\\
\hfill\textit{Best Design}
}

\end{paracol}

\end{document}
