%------------------------------------------------------------
% resume2.tex — Brian Hungerman
% Compile: pdflatex resume2.tex
%------------------------------------------------------------
\documentclass[10pt,letterpaper]{article}

\usepackage[top=0.2in, bottom=0.2in, left=0.38in, right=0.38in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{paracol}
\usepackage[T1]{fontenc}
\usepackage[default]{opensans}
\usepackage{microtype}
\usepackage{calc}

% Open Sans is now the default font (has sb/semi-bold weight)

% \sb = semi-bold for proper nouns & acronyms in descriptions
\newcommand{\semi}[1]{{\fontseries{sb}\selectfont #1}}

\hypersetup{
  colorlinks=false,
  pdfborder={0 0 0},
  pdfauthor={Brian Hungerman},
  pdftitle={Brian Hungerman -- Resume}
}

% ── Section headers: black rule ABOVE, then BOLD text ─────
\titleformat{\section}
  {\fontsize{10}{12}\selectfont\bfseries}
  {}
  {0pt}
  {\vspace{-2pt}\hrule height 0.5pt\vspace{4pt}\MakeUppercase}

\titlespacing*{\section}{0pt}{8pt}{2pt}

% ── Tight bullet lists ───────────────────────────────────
\setlist[itemize]{
  nosep, topsep=0pt, partopsep=0pt, parsep=0pt,
  itemsep=0pt, left=8pt, label={\textbullet},
  before=\vspace{-2pt}, after=\vspace{0pt}
}
\setlist[itemize,2]{
  nosep, topsep=0pt, partopsep=0pt, parsep=0pt,
  itemsep=0pt, left=10pt, label={$\cdot$}
}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\columnsep}{10pt}

\setlength{\columnseprule}{0.4pt}

% ══════════════════════════════════════════════════════════
\begin{document}

% ── HEADER ────────────────────────────────────────────────
\begin{minipage}[t]{0.62\textwidth}
  \vspace{0pt}
  {\fontsize{24}{28}\selectfont\bfseries Brian Hungerman}
\end{minipage}%
\hfill
\begin{minipage}[t]{0.34\textwidth}
  \vspace{0pt}
  \raggedleft\small
  https://brianhungerman.com\\
  brianhungerman@gmail.com\\
  1 (425) 389-9642
\end{minipage}

\vspace{1pt}

% ── TWO COLUMNS ──────────────────────────────────────────
\columnratio{0.77}
\begin{paracol}{2}

% ══════════════ LEFT COLUMN ══════════════════════════════

\section*{Experience}

\textbf{Senior Software Engineer @ Applied Sciences (Microsoft)} \hfill {\mdseries\small Jan 2025 -- Present}
\begin{itemize}
  \item Incubating novel A.I.\ user experiences with collaboration across W+D, MSR \& ID.
  \item Developing full-stack functional prototypes across web \& mobile platforms.
\end{itemize}
\vspace{3pt}
\textbf{Software Engineer @ A.I.\ Platform (Microsoft)} \hfill {\mdseries\small Jan 2020 -- Jan 2025}
\begin{itemize}
  \item Shipped \semi{Online Endpoints} to 50+ regions for \semi{Azure OpenAI}, \semi{Copilot}, \semi{Office} \& 3p.
  \item Scaled cloud infrastructure to serve trillions of inferences/month w/ 6 9's \semi{SLA}.
  \item Optimized \semi{Network Address Translation} to reduce \semi{COGS} by \$10 million/year.
  \item Completed security, privacy \& component governance audits as \semi{Security Champ}.
  \item Spearheaded livesite process improvements via \semi{TSGs} \& \semi{SOPs} as \semi{DRI Champ}.
  \item Implemented \semi{Envoy Proxy} build pipeline w/ \semi{Bazel} \& custom \semi{C++} filters, e.g.:
  \begin{itemize}
      \item \semi{SHA-256 Key-Based Authentication (KBA)} filter w/ \semi{CORS} preflight support.
      \item \semi{Azure Active Directory (AAD)} authentication filter w/ \semi{LRU} decision cache.
      \item \semi{Global Rate Limiting} filter w/ \semi{Go} microservice to pub/sub to \semi{Redis} cache.
  \end{itemize}
  \item Set up runners \& telemetry pipelines in \semi{Azure Data Explorer}, \semi{Kusto} \& \semi{SQL}.
  \item Shipped \semi{PowerBI} \& \semi{Grafana} dashboards to track platform metrics \& logs.
\end{itemize}
\vspace{3pt}
\textbf{Software Engineer Intern @ A.I.\ Platform (Microsoft)} \hfill {\mdseries\small May 2019 -- Aug 2019}
\begin{itemize}
  \item Designed \semi{Jupyter} notebook \semi{CI} pipeline w/ \semi{Azure DevOps}, \semi{ML SDK} \& \semi{Functions}.
\end{itemize}
\vspace{3pt}
\textbf{Software Engineer Intern @ Ventana (Roche)} \hfill {\mdseries\small May 2018 -- Dec 2018}
\begin{itemize}
  \item Pushed feature-adds \& bug-fixes for \semi{MEAN} stack digital pathology web app.
  \item Prototyped \semi{OpenSeaDragon}-esque image renderer \& annotator in \semi{Pixi.JS}.
  \item Modernized \semi{Nagios} server monitoring w/ \semi{Icinga}, \semi{Graphite} \& \semi{Grafana}.
\end{itemize}
\vspace{3pt}
\textbf{Director @ HackMerced IV (MLH)} \hfill {\mdseries\small May 2018 -- May 2019}
\begin{itemize}
  \item Hosted non-profit collegiate hackathon for 300 students, fundraising \$20,000!
\end{itemize}
\vspace{3pt}
\textbf{Web Developer @ CITRIS \& Banatao Institute (UCM)} \hfill {\mdseries\small May 2017 -- Dec 2018}
\begin{itemize}
  \item Developed \semi{GitOps} content management system (\semi{CMS}) via \semi{jQuery} \& \semi{CSV} files to replace \semi{Drupal} \semi{CMS}, hosting via \semi{GitHub Pages}: https://citris.ucmerced.edu.
\end{itemize}
\vspace{3pt}
\textbf{Instructor @ Summer of Game Design (MVHS)} \hfill {\mdseries\small Jun 2015 -- Jul 2016}
\begin{itemize}
  \item Co-founded non-profit game programming summer camp, fundraising \$25,000!
\end{itemize}

\section*{Research \& Education}

\textbf{Bachelor of Science @ University of California, Merced} \hfill {\mdseries\small Aug 2016 -- Dec 2019}
\begin{itemize}
  \item Computer Science \& Engineering, \textit{magna cum laude} (GPA 3.74)
\end{itemize}
\vspace{3pt}
\textbf{Lead Research Assistant @ VICE Lab (UCM)} \hfill {\mdseries\small Aug 2018 -- Dec 2019}
\begin{itemize}
  \item Led team to develop heuristic \& \semi{ML} scripts in \semi{Google Earth Engine} to model \& predict California's agricultural fallowing via Earth observation satellite data.
  \item Onboarded lab to \semi{GitHub} \& wrote open-sourced scripts in \semi{Python}, \semi{C\#} \& \semi{R}.
  \item Refurbished lab's website, hosting via \semi{GitHub Pages}: https://vicelab.net.
\end{itemize}
\vspace{3pt}
\textbf{Research Assistant @ ANDES Lab (UCM)} \hfill {\mdseries\small Jan 2019 -- May 2019}
\begin{itemize}
  \item Visualized \semi{InfluxDB} data for \semi{HVAC} predictive control system in \semi{Python}, \semi{Grafana}.
\end{itemize}
\vspace{3pt}
\textbf{Research Assistant @ SAIL + MACES (UCM \& NASA MUREP)} \hfill {\mdseries\small Aug 2017 -- May 2018}
\begin{itemize}
  \item Debugged code to 3D-print \semi{Fermi} surfaces via \semi{Marching cubes} in \semi{Fortran90}.
\end{itemize}

% ══════════════ RIGHT COLUMN ═════════════════════════════
\switchcolumn

\section*{Skills}

\scriptsize
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{Languages} & \textit{years} \\[1pt]
C / C++ / C\#       & 8 \\
Python              & 6 \\
JavaScript / TS     & 4 \\
Golang / Rust       & 2 \\
Java / Kotlin       & 2 \\[4pt]
\textbf{Frameworks} & \textit{years} \\[1pt]
Azure / .NET        & 6 \\
MEAN / MERN         & 2 \\
LAMP / Drupal       & 2 \\[4pt]
\textbf{Programs}   & \textit{years} \\[1pt]
Unity3D             & 8 \\
Docker / K8s        & 4 \\
Android Studio      & 2 \\
\end{tabular*}
\normalsize

\section*{Projects}

\scriptsize
\textbf{Iterate}\\
\textit{``Code Mobilized''}\\[2pt]
\textbf{BitNaughts}\\
\textit{``Code Gamified''}\\[2pt]
\textbf{MARP}\\
\textit{``\ldots''}
\normalsize

\section*{Awards}

\scriptsize
\textbf{Microsoft Hackathon '20}\\
\textit{HackADuo Finalist}\\[1pt]
\textbf{ValleyHacks '19}\\
\textit{First Place}\\[1pt]
\textbf{SLOHacks '19}\\
\textit{Best Google Cloud}\\[1pt]
\textbf{Mobile App Challenge '18}\\
\textit{\$2,000 Finalist Prize}\\[1pt]
\textbf{CitrusHack '18}\\
\textit{Third Place}\\[1pt]
\textbf{SDHacks '18}\\
\textit{Third Place}\\[1pt]
\textbf{SacHacks '18}\\
\textit{Second Place}\\[1pt]
\textbf{HackDavis '18}\\
\textit{Best Environment}\\[1pt]
\textbf{HackFresno '18}\\
\textit{Best Hardware}\\[1pt]
\textbf{Mobile App Challenge '17}\\
\textit{\$5,000 Grand Prize}\\[1pt]
\textbf{HackMerced '17}\\
\textit{Best Design}
\normalsize

\end{paracol}

\end{document}

